Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-08 appendix.tex
Commit 2023-11-08 17:10

\caption{Seasonla distribution of the SDR's long term trends by SZA before and after noon. The solid data points represent values with an acceptable statistical significance ($p<0.005$), the trends were computed with SZA bins of $1^\circ$ for each day, before and after local noon, all graphs have the same scale. Bins with $p<0.005$ or with less than 85 data points may be missing from the view.}\label{fig:SZAtrendSeason}
\end{figure}

>>>>

\caption{Seasonal distribution of the SDR's long term trends by SZA before and after noon. The solid data points represent values with an acceptable statistical significance ($p<0.005$), the trends were computed with SZA bins of $1^\circ$, before and after local noon. Bins where $p<0.005$ or with less than 85 data points may be missing from view.}\label{fig:SZAtrendSeason}
\end{figure}
